%-------------------------
% Resume in Latex
% Author : Aditya Lele
% License : IIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{lipsum}
%\usepackage{Times}
\usepackage{etaremune}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		%\textit{\small#5} & \textit{\small #6} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingtwo}[6]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} & \textit{\small #6} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\Large Aditya Dilip Lele}& Email : \href{mailto:al9001@princeton.edu}{al9001@princeton.edu}\\
		Princeton University&  \href{https://scholar.google.com/citations?user=McOb5L8AAAAJ&hl=en}{Google Scholar}\\
		 %& Mobile : +1-8148265092 \\
	\end{tabular*}

\section{Professional Summary}
Experienced computational chemist and materials scientist with expertise in molecular dynamics simulations, machine learning, and sustainable chemistry. Demonstrated track record of high-impact research in non-equilibrium catalysis, polymer decomposition, and renewable fuels, with 15+ publications including Nature and Nature Communications. Skilled in developing machine learning force fields and multi-scale modeling approaches for complex chemical systems. Strong background in combustion chemistry, plasma catalysis, and materials synthesis with applications in sustainable energy and environmental technologies.

\section{Research interests}

\begin{itemize}
	\item Molecular Simulations, Machine Learning and AI, Sustainable Chemistry and Materials Research
\end{itemize}

	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheadingtwo
	{The Pennsylvania State University}{State College, PA, USA}
	{\textbf{Ph. D.}  in Mechanical Engineering;  CGPA:3.93/4.0 }{Aug '18 -- Jul '21}
	{\textbf{Doctoral minor} in Computational Materials}{}
	\resumeSubheading
	{Indian Institute of Technology Madras}{Chennai, India}
	{\textbf{Master of Science} (by research) in Mechanical Engineering;  CGPA:8.8/10}{Jan '16 -- Jul '18}
	\resumeSubheading
	{Vishwakarma Institute of Technology}{Pune, India}
	{\textbf{Bachelor of Technology} in Mechanical Engineering;  CGPA: 9.31/10}{July '11 -- May '15}
	\resumeSubHeadingListEnd

	\section{Academic Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Postdoctoral Research Associate}{Princeton, NJ, USA}
{Princeton University}{Sept '21 -- present}

{Projects: Non-equilibrium NH$_3$ catalysis, Polymer decomposition, ML force fields}
\newline
{Faculty Mentor: Prof. Yiguang Ju}

\resumeSubheading
{Graduate Assistant}{State College, PA, USA}
{The Pennsylvania State University}{Aug '18 -- Jul '21}

{Projects: Combustion chemistry of renewable fuels, Carbon materials, 2D Material synthesis}
\newline
{Faculty Mentor: Prof. Adri van Duin}

\resumeSubheading
{Visiting Researcher}{Braunschweig, Germany}
{Physikalisch-Technische Bundesanstalt}{May '17 -- Jul '17}

{Projects: Reaction kinetics of methyl esters}
\newline
{Faculty Mentor: Dr. Kai Moshammer, Prof. Ravi Fernandez}

\resumeSubheading
{Research Scholar}{Chennai, India}
{Indian Institute of Technology Madras}{Jan '16 -- Jul '18}

{Projects: Pollutant formation in Biodiesel fueled engines}
\newline
{Faculty Mentor: Prof. Krithika Narayanaswamy, Prof. K. Anand}

\resumeSubHeadingListEnd	
	

	
	%-----------Research Output-----------------
	\section{Selected Publications 	(\small{\textit{*Equal contribution}},
		\small{\textit{$\#$Corresponding Author}}) }
	\begin{etaremune}%[start=1]
		\itemsep0em 
		\item Hua Xie , Ning Liu , Qian Zhang , Hongtao Zhong , Liqun Guo , Daozheng Li , Shufeng Liu , Zhennan Huang , \textbf{Aditya Lele} , Alexandra Brozena , Xizheng Wang , Keqi Song , Sophia Chen , Yan Yao , Miaofang Chi , Wei Xiong , Mikhail Shneider , Jian Luo , Ji-Cheng Zhao , Yiguang Ju.  	A Uniform, Ultrahigh-Temperature Plasma Operating at Atmospheric Pressure for the Synthesis of Extreme Materials.  (\textit{Accepted in \textbf{Nature}})		
		\item Qi Dong*, \textbf{Aditya Dilip Lele*}, Xinpeng Zhao*, Shuke Li*, Sichao Cheng, Yueqing Wang, Mingjin Cui et al. Depolymerization of plastics by means of electrified spatiotemporal heating. \textbf{\textit{Nature}} 616, no. 7957 (2023): 488-494.
		\item \textbf{Lele, Aditya Dilip$^\#$}, and Yiguang Ju. Assessment of the impact of reactor residence time distribution on non-equilibrium product selectivity of polypropylene pyrolysis using reactive molecular dynamics simulations. \textbf{\textit{Fuel}} 338 (2023): 127328.
		\item \textbf{Lele, Aditya Dilip$^\#$}, Yijie Xue and Yiguang Ju.  Modelling the effect of surface charging on plasma synthesis of ammonia using DFT. (\textit{Under review in \textbf{ACS Energy Letters}})
		\item \textbf{Lele, Aditya Dilip*$^\#$}, Qi Dong*, Liangbing Hu and Yiguang Ju.  Simulations driven selective non-equilibrium recycling of polyethylene (\textit{Under Review in \textbf{JAAP}})		
		\item \textbf{Lele, Aditya Dilip$^\#$}, Zhiyu Shi, John Mark Martirez, Emily A. Carter, Yiguang Ju. Exploring NH$_3$ synthesis under non-equilibrium conditions. (\textit{Under Preperation})
		\item \textbf{Lele, Aditya}, Predrag Krstic, and Adri CT van Duin. "ReaxFF Force Field Development for Gas-Phase hBN Nanostructure Synthesis." The \textbf{\textit{Journal of Physical Chemistry A}} (2022).
		\item \textbf{Lele, Aditya}, Hyunguk Kwon, Karthik Ganeshan, Yuan Xuan, and Adri CT van Duin. (2021). ReaxFF molecular dynamics study on pyrolysis of bicyclic compounds for aviation fuel. \textbf{\textit{Fuel}}, 297, 120724.
		\item \textbf{Lele, Aditya Dilip}, Sonal K. Vallabhuni, Kai Moshammer, Ravi X. Fernandes, Anand Krishnasamy, and Krithika Narayanaswamy. "Experimental and chemical kinetic modeling investigation of methyl butanoate as a component of biodiesel surrogate." \textit{\textbf{Combustion and Flame}} 197 (2018): 49-64.
	\end{etaremune}

	%-----------Research Output-----------------
\section{Selected Conferences and Presentations}
\begin{etaremune}
	\itemsep0em 
		\item  \textbf{Aditya Lele}, Zhiyu Shi, John Mark Martirez, Emily A. Carter, Yiguang Ju ``Machine learning force field for molecular dynamics simulation of non-equilibrium NH$_3$ synthesis on Fe 110",  ACS Fall 2023.
		\item  \textbf{Aditya Lele}, Qi Dong, Liangbing Hu, and Yiguang Ju. ``Molecular dynamics simulations for understanding and improving non-equilibrium plastic recycling product selectivity",  ACS Fall 2023.
		\item  Yijie Xu, Ning, Liu, \textbf{Aditya  Lele}, Yiguang Ju ``Ferroelectrics-induced surface charge effect on plasma dynamics and catalytic synthesis of NH$_3$",  ACS Fall 2023.
		\item  Zhiyu Shi,  \textbf{Aditya Dilip Lele}, Ahren Jasper, Stephen Klippenstein, Yiguang Ju ``Quasi-classical trajectory calculation of rate constant using ab-initio trained machine learning force field (aML-MD)",  ACS Fall 2023.
	\item Christopher Burger, \textbf{Aditya Dilip Lele}, Zhiyu Shi, Yiguang Ju, ``Simulating supercritical pressure jet stirred reactor (SP-JSR) conditions for propane oxidation with real-gas
	effects through reactive molecular dynamics (ReaxFF)". US National combustion meeting, WIPP 2023.
	\item  \textbf{Aditya Lele}, Ying Lin, and Yiguang Ju. ``Understanding the significance of plasma-induced surface charging on ammonia synthesis through DFT modelling",  ACS Fall 2022.
	\item  \textbf{Aditya Lele}, Kwon, Hyunguk, Junqing Zhu, Charles S. McEnally, Lisa D. Pfefferle, Yuan Xuan, and Adri CT van Duin. ``ReaxFF-based molecular dynamics study of bio-derived polycyclic alkanes as potential alternative jet fuels.",  Future of Bioenergy and Biorenewables poster session (2020), The Pennsylvania State University. \textbf{(3rd place prize)}
\end{etaremune}	

	%-----------Teaching and Mentoring-----------------
	\section{Teaching and Mentoring}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Teaching: Practical molecular simulations}{}
	{Princeton University}{Fall '22}
	
	{\textbf{Designed and taught 50$\%$ of a graduate class:} Prepared teaching materials, projects and assignments. Delivered lectures and hands-on tutorials. Developed a course website to promote active learning.}
	
	\resumeSubheading
	{Teaching assistant: Indoor Air Quality Engineering }{}
	{The Pennsylvania State University}{Fall '18}
	
	\resumeSubheading
	{Teaching assistant: Numerical Methods for Thermal Engineering}{}
	{Indian Institute of Technology Madras}{Spring '17}

	\resumeSubheading
	{Summer internship program}{}
	{Princeton University}{Summer '22, '23}

	{\textbf{Sophia Chen}, Project: DFT calculations for catalysis}	\newline
	{\textbf{Eileen Wang}, Project: Understanding nitride formation in metals using molecular simulations. }	\newline
	{\textbf{Shrey Khetan}, Project: ML force fields for NH$_3$ gas-phase chemistry. }	\newline
	{\textbf{Desiree Rivers}, Project: DFT exploration of ferroelectric materials. }	

	\resumeSubheading
	{Christopher Berger(Ph. D. student)}{}
	{Princeton University}{Fall '22 -- Spring '23}

	{Project: Modelling supercritical combustion effects using molecular dynamics}\newline
	{Outcome: WIPP poster at 13th US national Combustion Meeting.}
	
	\resumeSubheading
	{Zhiyu Shi: (Ph. D. student)}{}
	{Princeton University}{Fall '22 -- current}

	{Project: Transfer learning potential energy surface for rate constant prediction}\newline
	{Outcome: Manuscript under preparation.}
	
	\resumeSubHeadingListEnd

	\section{Technical Skills and Honors}
\begin{itemize}
	\itemsep0em 
	\item \textbf{Simulation tools:} FlameMaster, ChemKin, Forte, ReaxFF, LAMMPS, Gaussian, VASP, CP2K
	\item \textbf{Programming Languages:} C++, Perl
	\item \textbf{Other:} Linux, \LaTeX, MS Excel, MATLAB
\end{itemize}

\resumeSubHeadingListStart
\resumeSubheading
{Scholarship for a short term research stay in Germany}{}
{Indo-German Centre for Sustainability}{Summer '17}

\resumeSubheading
{National Talent Search Examination Scholarship}{}
{Government of India}{'08 -- '15}

{One among 750 students from a pool of about 350,000 students}

\resumeSubHeadingListEnd

	\section{Leadership and Service}
\resumeSubHeadingListStart
\resumeSubheading{Peer Review}{}
{Scientific journals and conferences}{}
\begin{itemize}
	\item Combustion and Flame, Fuel, Applied Energy, Proceedings of the combustion institute, ACS applied nano materials, Journal of Analytical and Applied Pyrolysis 
\end{itemize}
\resumeSubheading{Session moderator}{Washington DC}
{DOE Annual Meeting of the LTP(Low-temperature Plasma) Centers and User Facilities}{Oct '22}
\resumeSubheading{Summer school organizer}{Princeton, NJ}
{Asian American Association for Science Engineering}{Summer '22, '23}
\begin{itemize}
	\item Helped organize science and technology focused summer school for high-school students.
	\item Organized and lead group project activity.
\end{itemize}	

\resumeSubHeadingListEnd

\section{Industry Experience}
\resumeSubHeadingListStart
\resumeSubheading{Eaton India Pvt. Ltd.}{Pune, India}
{Project: Gear shift quality assessment tool development in MS Excel}{Jul '15 -- Dec '15}
\resumeSubheading{Panse Autocomp Pvt. Ltd.}{Pune, India}
{Internship Project: Single minute exchange process of die for manufacturing automobile components.}{May '13 -- Jul '13}	
\resumeSubHeadingListEnd	

\end{document}